Cosmology with photometric weak lensing surveys: constraints with redshift tomography of convergence peaks and moments

### 2016-05-02 photoz_paper/paper.tex
update abstract/acknowledgements

\begin{abstract}
Weak gravitational lensing is becoming a mature technique for constraining cosmological parameters, and future surveys will be able to constrain the dark energy equation of state $w$. When analyzing galaxy surveys, redshift information has proven to be a valuable addition to angular shear correlations. We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for an LSST-like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments. We find that redshift tomography with the power spectrum shrinks the $1\sigma$ confidence interval area in $(\Omega_m,w)$ space by a factor of 8 with respect to the case of the single highest redshift bin. We also find that adding non-Gaussian information from the peak counts and higher moments of the convergence further shrinks the constrained area in $(\Omega_m,w)$ by a factor of respectively 3 and 4. When we add parameter priors from Planck to our analysis, tomography improves power spectrum constraints by a factor of 3. Adding moments improves by an additional factor of 2, and  adding both moments and peaks improves by almost a factor of 3 over power spectrum tomography alone. We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints. We find that different statistics lead to different bias directions in parameter space, suggesting the possibility of eliminating this bias via self-calibration. 
\end{abstract}

@@

Most of the calculations were performed at National Energy Research Scientific Computing Center (NERSC). We thank the LSST Dark Energy Science Collaboration (DESC) for the allocation of time, and for many useful discussions. We thank Hu Zhan, Salman Habib, Jeffrey Newman, Deborah Bard, and Peter Nugent for technical help. We thank Colin Hill and Licia Verde for useful discussions. We also thank Martin Kilbinger and Lloyd Knox for comments on an earlier version of this manuscript.
Part of the simulations in this work were also performed at the NSF XSEDE facility, supported by grant number
ACI-1053575, and at the New York Center for Computational Sciences, a
cooperative effort between Brookhaven National Laboratory and Stony
Brook University, supported in part by the State of New York. This
work was supported in part by the U.S. Department of Energy under
Contract Nos. DE-AC02-98CH10886 and DE-SC0012704, and by the NSF Grant
No. AST-1210877 (to Z.H.) and by the Research Opportunities and
Approaches to Data Science (ROADS) program at the Institute for Data
Sciences and Engineering at Columbia University (to Z.H.).

>>>>

\begin{abstract}
Weak gravitational lensing is becoming a mature technique for
constraining cosmological parameters, and future surveys will be able
to constrain the dark energy equation of state $w$. When analyzing
galaxy surveys, redshift information has proven to be a valuable
addition to angular shear correlations. We forecast parameter
constraints on the triplet $(\Omega_m,w,\sigma_8)$ for an LSST-like
photometric galaxy survey, using tomography of the shear-shear power
spectrum, convergence peak counts and higher convergence moments. We
find that redshift tomography with the power spectrum reduces the area
of the $1\sigma$ confidence interval in $(\Omega_m,w)$ space by a
factor of 8 with respect to the case of the single highest redshift
bin. We also find that adding non-Gaussian information from the peak
counts and higher-order moments of the convergence field and its
spatial derivatives further reduces the constrained area in
$(\Omega_m,w)$ by a factor of 3 and 4, respectively. When we add
cosmic microwave background parameter priors from Planck to our
analysis, tomography improves power spectrum constraints by a factor
of 3. Adding moments yields an improvement by an additional factor of
2, and adding both moments and peaks improves by almost a factor of 3,
over power spectrum tomography alone. We evaluate the effect of
uncorrected systematic photometric redshift errors on the parameter
constraints. We find that different statistics lead to different bias
directions in parameter space, suggesting the possibility of
eliminating this bias via self-calibration. 
\end{abstract}

@@

We thank Hu Zhan, Salman Habib, Jeffrey Newman, Colin Hill and Licia Verde for useful discussions. We also thank Martin Kilbinger and Lloyd Knox for comments on an earlier version of this manuscript. Most of the calculations were performed at National Energy Research Scientific Computing Center (NERSC). We thank the LSST Dark Energy Science Collaboration (DESC) for the allocation of time, and for many useful discussions. 
Part of the simulations in this work were also performed at the NSF XSEDE facility, supported by grant number
ACI-1053575, and at the New York Center for Computational Sciences, a
cooperative effort between Brookhaven National Laboratory and Stony
Brook University, supported in part by the State of New York. This
work was supported in part by the U.S. Department of Energy under
Contract No. DE-SC00112704, and by the NSF Grant
No. AST-1210877 (to Z.H.) and by the Research Opportunities and
Approaches to Data Science (ROADS) program at the Institute for Data
Sciences and Engineering at Columbia University (to Z.H.).
